\chapter{Simulation results}
\label{chap:simulation}

This chapter shows simulation results to compare the use of the TSL model
against more naive approaches to the matching problems.

Table for the values underlying the simulation results

Table / Graph showing the result of the TSL vs one sided logit

Discuss how to do interpretation

Simulate a change in one side leading to a wrong estimate of the other side
- Logan shows the change in the demand (i.e. the demand intercept)
- Maybe I could show the change in the preference for characteristics?
- This kind of simulation can be done again for FDI later

Discuss the effect of having offers that are different across respondents

Discuss the correlation of MCMC

Discuss the adaptive procedure that I attempted but failed

The reason for the high degree of correlation is because beta and opp is highly
correlated
- We can't change the opp a lot, because conditional on beta, the opp is kinda
stuck. If we flip opp too much, it will be rejected because it'd be too
inconceivable given the current state of beta (may be make a graph here of the
rejection rate for opp)
- We can't change the beta a lot because conditional on opp, it's also kinda
stuck. This is especially true for countries with only a few observation of
firms invested in them.
Because if a country only has 5 firms in, if we flip the opp so that now the
country extends the offer to a new firm, and this firm is substantially
different from the current ones, that will really affect the estimate for beta.
For countries with a lot of firms invested in them, we can already estimate
their preference quite well, so flipping a new opp doesn't change the estimate
too much.
- Conceptually, we can think of a way to make proposal for beta and opp that
takes into account this correlation. For example, if we propose a new beta that
puts a high emphasis on employment, then we also are more likely to flip (to 1)
the cells that correspond to firms that have a large amount of employees.
However this is a bit too hard to implement and the computation cost may not be
worth it.

- The Gibbs sampler approach may work? But it's also unable to make correlated
move so may not be so much better.